R code from PRACTICE sections

### 2024-07-01 rcode.qmd
Built site for gh-pages

@@

```{r}
library(tidyverse)
set.seed(1)
dat <- simulate(n_subjects = 500, n_items = 500,
  sd_u0s = 0.5, sd_u0i = 0.5)
dat %>% 
  mutate(condition = fct_cross(
    factor(expert), factor(advice_present), factor(advice_correct))) %>%
  mutate(condition = fct_recode(condition,
    "no expert, no advice" = "0:0:0", "expert, no advice" = "1:0:0", 
    "no expert, wrong advice" = "0:1:0", "expert, wrong advice" = "1:1:0",
    "no expert, correct advice" = "0:1:1", "expert, correct advice" = "1:1:1")) %>% 
  group_by(condition) %>%
  summarize(relative_frequency = sum(y_bin) / n())
```

@@

library(ggdist)
dat %>% 
  mutate(condition = fct_cross(
    factor(expert), factor(advice_present), factor(advice_correct))) %>%
  mutate(condition = fct_recode(condition,
    "no expert, no advice" = "0:0:0", "expert, no advice" = "1:0:0", 
    "no expert, wrong advice" = "0:1:0", "expert, wrong advice" = "1:1:0",
    "no expert, correct advice" = "0:1:1", "expert, correct advice" = "1:1:1")) %>% 
  ggplot(aes(x = y_prob, y = condition)) +
  stat_histinterval(point_interval = "mean_qi", slab_color = "gray45") +
  scale_x_continuous(breaks = seq(0, 1, 0.1), limits = c(0, 1))
```

```{r}
#| label: fig-margdist2
#| fig-cap: "Marginal distributions including means, 66% and 95% confidence intervals for all experimental conditions while setting the standard deviation of item random intercepts to 0.01."
set.seed(1)
dat <- simulate(n_subjects = 500, n_items = 500, sd_u0i = 0.01)
dat %>% 
  mutate(condition = fct_cross(
    factor(expert), factor(advice_present), factor(advice_correct))) %>%
  mutate(condition = fct_recode(condition,
    "no expert, no advice" = "0:0:0", "expert, no advice" = "1:0:0", 
    "no expert, wrong advice" = "0:1:0", "expert, wrong advice" = "1:1:0",
    "no expert, correct advice" = "0:1:1", "expert, correct advice" = "1:1:1")) %>% 
  ggplot(aes(x = y_prob, y = condition)) +
  stat_histinterval(point_interval = "mean_qi", slab_color = "gray45") +
  scale_x_continuous(breaks = seq(0, 1, 0.1), limits = c(0, 1))
```

```{r}
#| include: false
set.seed(1)
dat <- simulate(n_subjects = 500, n_items = 500, sd_u0s = 0.01)
dat %>% 
  mutate(condition = fct_cross(
    factor(expert), factor(advice_present), factor(advice_correct))) %>%
  mutate(condition = fct_recode(condition,
    "no expert, no advice" = "0:0:0", "expert, no advice" = "1:0:0", 
    "no expert, wrong advice" = "0:1:0", "expert, wrong advice" = "1:1:0",
    "no expert, correct advice" = "0:1:1", "expert, correct advice" = "1:1:1")) %>% 
  ggplot(aes(x = y_prob, y = condition)) +
  stat_histinterval(point_interval = "mean_qi", slab_color = "gray45") +
  scale_x_continuous(breaks = seq(0, 1, 0.1), limits = c(0, 1))
```

```{r}
#| label: fig-margdist3
#| echo: false
#| fig-cap: "Marginal distributions including means, 66% and 95% confidence intervals for all experimental conditions while setting the standard deviation of subject and item random intercepts to 3."
set.seed(1)
dat <- simulate(n_subjects = 500, n_items = 500, sd_u0s = 3, sd_u0i = 3)
dat %>% 
  mutate(condition = fct_cross(
    factor(expert), factor(advice_present), factor(advice_correct))) %>%
  mutate(condition = fct_recode(condition,
    "no expert, no advice" = "0:0:0", "expert, no advice" = "1:0:0", 
    "no expert, wrong advice" = "0:1:0", "expert, wrong advice" = "1:1:0",
    "no expert, correct advice" = "0:1:1", "expert, correct advice" = "1:1:1")) %>% 
  ggplot(aes(x = y_prob, y = condition)) +
  stat_histinterval(point_interval = "mean_qi", slab_color = "gray45") +
  scale_x_continuous(breaks = seq(0, 1, 0.1), limits = c(0, 1))
```

@@

```{r}
pred_df <- data.frame(advice_present = c(1, 0), advice_correct = c(1, 0), 
  expert = c(1, 1))
pred_df
preds <- predict(fit, newdata = pred_df, type = "response", re.form = NA)
preds
preds[1] - preds[2]
```

```{r}
library(tidyverse)
library(marginaleffects)
pred_df <- expand_grid(advice_present = 0:1, advice_correct = 0:1, expert = 0:1)
pred_df
probs <- predictions(fit, newdata = pred_df, type = "response", re.form = NA)
probs
```

```{r}
probs %>% 
  hypotheses(hypothesis = c(
    "b8 = b2",
    "b2 = b6",
    "b7 = b1",
    "b1 = b5"),
    equivalence = c(0, 0))
```

>>>>

## Specify the population parameters

@@

```{r}
library(tidyverse)
set.seed(1)
dat <- simulate(n_subjects = 500, n_items = 500,
  sd_u0s = 0.5, sd_u0i = 0.5)
dat %>% 
  mutate(condition = fct_cross(
    factor(expert), factor(advice_present), factor(advice_correct))) %>%
  mutate(condition = fct_recode(condition,
 "student, no advice" = "0:0:0", "expert, no advice" = "1:0:0", 
 "student, incorrect advice" = "0:1:0", "expert, incorrect advice" = "1:1:0",
 "student, correct advice" = "0:1:1", "expert, correct advice" = "1:1:1")) %>% 
  group_by(condition) %>%
  summarize(relative_frequency = sum(y_bin) / n())
```

@@

library(ggdist)
dat %>% 
  mutate(condition = fct_cross(
    factor(expert), factor(advice_present), factor(advice_correct))) %>%
  mutate(condition = fct_recode(condition,
"student, no advice" = "0:0:0", "expert, no advice" = "1:0:0", 
"student, incorrect advice" = "0:1:0", "expert, incorrect advice" = "1:1:0",
"student, correct advice" = "0:1:1", "expert, correct advice" = "1:1:1")) %>% 
  ggplot(aes(x = y_prob, y = condition)) +
  stat_histinterval(point_interval = "mean_qi", slab_color = "gray45",
    breaks = "Sturges") +
  scale_x_continuous(breaks = seq(0, 1, 0.1), limits = c(0, 1))
```

```{r}
#| label: fig-margdist2
#| fig-cap: "Marginal distributions including means, 66% and 95% confidence intervals for all experimental conditions while setting the standard deviation of item random intercepts to 0.01."
set.seed(1)
dat <- simulate(n_subjects = 500, n_items = 500, sd_u0i = 0.01)
dat %>% 
  mutate(condition = fct_cross(
    factor(expert), factor(advice_present), factor(advice_correct))) %>%
  mutate(condition = fct_recode(condition,
"student, no advice" = "0:0:0", "expert, no advice" = "1:0:0", 
"student, incorrect advice" = "0:1:0", "expert, incorrect advice" = "1:1:0",
"student, correct advice" = "0:1:1", "expert, correct advice" = "1:1:1")) %>% 
  ggplot(aes(x = y_prob, y = condition)) +
  stat_histinterval(point_interval = "mean_qi", slab_color = "gray45",
    breaks = "Sturges") +
  scale_x_continuous(breaks = seq(0, 1, 0.1), limits = c(0, 1))
```

```{r}
#| include: false
set.seed(1)
dat <- simulate(n_subjects = 500, n_items = 500, sd_u0s = 0.01)
dat %>% 
  mutate(condition = fct_cross(
    factor(expert), factor(advice_present), factor(advice_correct))) %>%
  mutate(condition = fct_recode(condition,
"student, no advice" = "0:0:0", "expert, no advice" = "1:0:0", 
"student, incorrect advice" = "0:1:0", "expert, incorrect advice" = "1:1:0",
"student, correct advice" = "0:1:1", "expert, correct advice" = "1:1:1")) %>% 
  ggplot(aes(x = y_prob, y = condition)) +
  stat_histinterval(point_interval = "mean_qi", slab_color = "gray45",
    breaks = "Sturges") +
  scale_x_continuous(breaks = seq(0, 1, 0.1), limits = c(0, 1))
```

```{r}
#| label: fig-margdist3
#| echo: false
#| fig-cap: "Marginal distributions including means, 66% and 95% confidence intervals for all experimental conditions while setting the standard deviation of subject and item random intercepts to 3."
set.seed(1)
dat <- simulate(n_subjects = 500, n_items = 500, sd_u0s = 3, sd_u0i = 3)
dat %>% 
  mutate(condition = fct_cross(
    factor(expert), factor(advice_present), factor(advice_correct))) %>%
  mutate(condition = fct_recode(condition,
"student, no advice" = "0:0:0", "expert, no advice" = "1:0:0", 
"student, incorrect advice" = "0:1:0", "expert, incorrect advice" = "1:1:0",
"student, correct advice" = "0:1:1", "expert, correct advice" = "1:1:1")) %>% 
  ggplot(aes(x = y_prob, y = condition)) +
  stat_histinterval(point_interval = "mean_qi", slab_color = "gray45",
    breaks = "Sturges") +
  scale_x_continuous(breaks = seq(0, 1, 0.1), limits = c(0, 1))
```

@@

```{r}
grid1 <- data.frame(advice_present = c(1, 0), advice_correct = c(1, 0), 
  expert = c(1, 1))
grid1
pred <- predict(fit, newdata = grid1, type = "response", re.form = NA)
pred
pred[1] - pred[2]
```

```{r}
library(marginaleffects)
library(tinytable)
grid2 <- expand_grid(advice_present = 0:1, 
  advice_correct = 0:1, expert = 0:1)
grid2
preds <- predictions(fit, newdata = grid2, 
  type = "response", re.form = NA)
print(preds, style = "tinytable") %>% theme_tt(theme = "resize")
```

```{r}
contrasts <- preds %>% 
  hypotheses(hypothesis = c(
    "b8 = b2",  # (correct advice, expert) - (no advice, expert)
    "b2 = b6",  # (no advice, expert) - (incorrect advice, expert) 
    "b7 = b1",  # (correct advice, student) - (no advice, student)
    "b1 = b5"), # (no advice, student) - (incorrect advice, student)
    equivalence = c(0, 0))
print(contrasts, style = "tinytable") %>% theme_tt(theme = "resize")
```
